### 2010-03-10 docs/managing_jobs/managingjobs.tex
update job-chaining magic for atlas

This allows you to job-chain a bunch of submission and have them wait
until the previous job finished and then automatically queue up:
\begin{verbatim}
qsub -W depend=afterany:<JOB-ID>  <QSUB SCRIPT>
\end{verbatim}

This way you can queue up a bunch of runs and literally leave things
alone and it will restart from the right place automatically and store
the data as it is generated.

@@

Analogous scripts exist for running on Atlas, with the same general
procedure.

>>>>

This allows you to job-chain a bunch of submission and have them wait
until the previous job finished and then automatically queue up:
\begin{verbatim}
qsub -W depend=afterany:<JOB-ID>  <QSUB SCRIPT>
\end{verbatim}
where {\tt <JOB-ID>} is the id number of the job that must complete
before the new submission runs and {\tt QSUB SCRIPT} is the submission
script (e.g.\ {\tt jaguar.run}).
This way you can queue up a bunch of runs and literally leave things
alone and it will restart from the right place automatically and store
the data as it is generated.

@@

Analogous scripts exist for running on Atlas, with the same general
procedure.  The command to chain a job on atlas is:
\begin{verbatim}
msub -l depend=<JOB-ID> <MSUB SCRIPT>
\end{verbatim}
where, again, {\tt <JOB-ID>} is the id number of the job that must
complete before the current submission runs and {\tt <MSUB SCRIPT>}
is the job submission script (e.g.\ {\tt atlas.run}).
